Visualizing Example of Clustered Predicted TAD Boundary Regions

### 2019-08-28 Scripts/visualizing_example_predicted_tad_bounds.Rmd
editted plotting parameters

ggplot() + 
  geom_line(data=predprobdata2, aes(x=basenum, y=prob), 
            color='black',
            size=.5)+
  geom_vline(data=calleddata, aes(xintercept=basenum, 
                                  color="blue"),
             size=.75,
             show.legend = TRUE)+
  geom_vline(data=predicteddata, aes(xintercept=basenum, 
                                     color="red"),
             size=.75,
             show.legend = TRUE)+
  xlab("Base Pair") +
  ylab("Predicted Probability") +
  scale_color_manual(name = '', 
                     values =c("blue", "red"),
                     labels = c("Called Boundary", 'Predicted Region'))+
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

@@

>>>>

ggplot() + 
  geom_line(data=predprobdata2, aes(x=basenum, y=prob), 
            color='black',
            size=.5)+
  geom_vline(data=calleddata, aes(xintercept=basenum, 
                                  color="blue"),
             size=.75,
             show.legend = TRUE)+
  geom_vline(data=predicteddata, aes(xintercept=basenum, 
                                     color="red"),
             size=.75,
             show.legend = TRUE)+
  xlab("Base Pair") +
  ylab("Probability") +
  scale_color_manual(name = '', 
                     values =c("blue", "red"),
                     labels = c("Called Boundary", 'Predicted Region'))+
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

@@

ggplot() + 
  geom_line(data=predprobdata2, aes(x=basenum, y=prob), 
            color='black',
            size=.5)+
  geom_vline(data=calleddata, aes(xintercept=basenum, 
                                  color="blue"),
             size=.75,
             show.legend = TRUE)+
  geom_vline(data=predicteddata, aes(xintercept=basenum, 
                                     color="red"),
             size=.75,
             show.legend = TRUE)+
  geom_vline(data=predicteddata2, aes(xintercept=basenum, 
                                      color="green"),
             size=.75,
             show.legend = TRUE)+
  xlab("Base Pair") +
  ylab("Probability") +
  scale_color_manual(name = '', 
                     values =c("blue", "green", "red"),
                     labels = c("Called Boundary",
                                "Predicted Boundary",
                                "Predicted Region"))+
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")
